Plug-and-play dual-tree algorithm runtime analysis

### 2015-08-14 bounds-files/imbalance.tex
Some minor last-minute changes.
Add empirical imbalance numbers.

\begin{figure}
\begin{center}
  \input{figures/multiple-outlier-tree.tex}
\end{center}
\caption{A badly-drawn multiple-outlier cover tree.}
\label{fig:outliers}
\end{figure}

@@

However, for most real-world datasets with the cover tree implementation in {\bf
mlpack} \citep{mlpack2013} and the reference implementation
\citep{langford2006}, the tree imbalance is near-linear with the number of
points.  Generally, most of the cover tree imbalance is contributed by leaf
nodes whose parent has scale greater than $s_{\min}$.  At this time, no cover
tree construction algorithm specifically aims to minimize imbalance.

>>>>

\begin{figure}
\begin{center}
  \input{figures/multiple-outlier-tree.tex}
\end{center}
\caption{A multiple-outlier cover tree.}
\label{fig:outliers}
\end{figure}

@@

However, for most real-world datasets with the cover tree implementation in {\bf
mlpack} \citep{mlpack2013} and the reference implementation
\citep{langford2006}, the tree imbalance is near-linear with the number of
points; see Table \ref{tab:imbalance} for empirically-calculated imbalances
on a number of datasets.  The `power', `susy', `higgs', and
`covertype' datasets are found in the UCI Machine Learning Repository
\cite{ucimlrepository}, the `mnist' dataset is from \cite{lecun2000mnist}, and
the `sdss' dataset is Sloan Digital Sky Survey data \cite{adelman2008sixth}.
Imbalance is shown for subsets of the datasets of size $5000$, $50000$, and
$500000$; the actual value of the imbalance is of less importance than the
scaling properties with $N$---which tend to be near-linear.

Currently, no cover tree construction algorithm specifically aims to minimize
imbalance.

\begin{table}[tb]
\begin{center}
\begin{tabular}{| c | c | c | c | c |}
\hline
 & & \multicolumn{3}{|c|}{Imbalance} \\
\hline
Dataset & $d$ & $N = 5k$ & $N = 50k$ & $N = 500k$ \\
\hline
%lcdm & 3 & 29402 & 313190 & 3400305 \\
sdss & 4 & 17691 & 191716 & 1483711 \\
power & 7 & 22152 & 202050 & 1345825 \\
susy & 18 & 3686 & 64231 & 930969 \\
higgs & 29 & 404 & 1272 & 73793 \\
covertype & 55 & 9680 & 100344 & 1319447 \\
mnist & 784 & 4004 & 79375 & 983554 \\
\hline
\end{tabular}
\end{center}
\caption{Empirically calculated tree imbalances.}
\label{tab:imbalance}
\end{table}
